\class : Problem Set \psetnum

### 2022-04-05 531_stars/pset1/solutions.tex
create new title style, add last question

\title{Astro 531; Problem Set 1}
\author{\textbf{Tom Wagg}}

@@

\maketitle

@@

\question{Part a - Radi  us}
\answer{
    \begin{align}
        L &= 4 \pi R^2 \sigma T_{\rm eff}^4 \\
        R &= \sqrt{\frac{L}{4 \pi \sigma T_{\rm eff}^4}} \\
        \Aboxed{ R &= 2570 \unit{R_{\odot}} }
    \end{align}
}

@@

% \clearpage

@@

>>>>

\newcommand{\psetnum}{1}
\newcommand{\class}{ASTR 531 - Stellar Interiors}

\newcommand{\tomtitle}{
    \noindent {\huge \fontfamily{cmr}\selectfont \textbf{\class}} \hfill \\[1\baselineskip]
    \noindent {\large \fontfamily{cmr}\selectfont Problem Set \psetnum \hfill \textsc{Tom Wagg}}\\[0.5\baselineskip]
    {\fontfamily{cmr}\selectfont \textit{\today}}\\[2\baselineskip]
}

\title{\class : Problem Set \psetnum}
\author{\textbf{Tom Wagg}}

@@

\tomtitle

@@

\question{Part a - Radius}
\answer{
    \begin{align}
        L &= 4 \pi R^2 \sigma T_{\rm eff}^4 \\
        R &= \sqrt{\frac{L}{4 \pi \sigma T_{\rm eff}^4}} \\
        \Aboxed{ R &= 2570 \unit{R_{\odot}} }
    \end{align}
}

@@

@@

\question{\textbf{7.2 - Convection Criterions}}

\question{Part a and Part b - Convection zones with different criterions}
\answer{
    I combined these two parts since I put all of the information on the same plot:
    \begin{center}
        \includegraphics[width=0.5\textwidth]{figures/criterion_shift_zones.jpg}
    \end{center}
    The $\mu$ profile decreases with increasing radius since fusion is creating heavier elements in the core. As the question asks I adopted some arbitrary limits (red lines) for the convection zone when using the Schwarzschild criterion.

    When instead adopting the Ledoux criterion, the convection zone will shrink (as shown by the green lines). I have two qualitative arguments for this. First, since the Ledoux criterion is identical to the Schwarzschild criterion except with an extra term for the $\mu$ gradient, this criterion is \textit{harder} to fulfill. This means that the fraction of the star that is convective should decrease and thus the zone should shrinks.

    Additionally, I also considered the `blob' of gas. When switching from Schwarzschild to Ledoux, a `blob' travelling upwards now is not only at a different temperature than the surrounding regions, but also probably heavier due to the increased $\mu$ relative to the surroundings. This would decrease the upper limit of the convection zone since a `blob' could not travel to the same height. The same argument can be applied in the opposite direction and so a `blob' can't sink as far into the star, increasing the lower limit.
}

\question{Part c - Convection effects on $\mu$ gradient}
\answer{
    The $\mu$ gradient flattens out within the convection zone. This is because all of the material is mixed and thus the $\mu$ at all radii within the zone because the average of the $\mu$ values that were in the zone initially. See the image below for my sketch of this.
    \begin{center}
        \includegraphics[width=0.7\textwidth]{figures/mixing.jpg}
    \end{center}
}
